Concave reduction of swarm voids

### 2018-06-05 paper.tex
IEEE Access Modifications
New Section

\section{Swarm coordination - concave reduction}\label{chapter:ConcaveReduction}
When cohesion and repulsion (\textit{inter-agent vectors}) are the only field effects creating a swarming effect the number of stable structures that can develop is limited. These structures are either straight edges or partial lattices. Partial lattices can create concave anomalies (dents) and convex anomalies (peaks) in a perimeter~(Fig.~\ref{concave:SwarmStableShape1}). An anomaly is any construct within the swarm that is not a hexagonal lattice or an agent distribution that causes the swarm to deviate from having only convex or flat edges.

@@

@@

@@

When discussing concave reduction the concave angle of interest is the relationship between an agent and two of its adjacent neighbours such that the neighbours have no visibility of each other and the neighbour-agent-neighbour relationship produces an angle~$< 180^\circ$. This is unrelated to the aggregate angle used to identify the perimeter type that the agent is a member of. Concave reduction therefore affects both inner~(Fig.~\ref{fig:InnerPerimeter1}) and outer~(Fig.~\ref{fig:OuterPerimeter1}) perimeter agents. Fig.~\ref{fig:OuterPerimeter1} and \ref{fig:InnerPerimeter1} show candidate agents identified by this process in black.

@@

The purpose of concave reduction is to alter the overall structure of the swarm by replacing the calculated \textit{movement-direction vector} on anomalous perimeter agents. These perimeter based changes cause a cascading movement within the swarm as non-perimeter based agent's \textit{interaction vectors} attempting to move towards a position of equilibrium to their neighbours. The movement of the concave-perimeter~(internal void) agents creates a tendency for the void to be removed~(Fig.~\ref{fig:InnerPerimeter2}~and~\ref{fig:InnerPerimeter3}) by percolating the void out of the swarm. On the outer perimeter deformities (indents) are straightened~(Fig.~\ref{fig:OuterPerimeter3}) and eventually a perimeter agent and its neighbours will tend towards creating a convex edge.

@@

\begin{equation}
S_b \buildrel \Delta \over = \{(b',\angle\{(b'~b~b^0)) : b' \in nbr(b)\}\}
\label{eq:ConcaveVoidPhysics1}
\end{equation}

>>>>

\section{Introduction}\label{sec:ConcaveReduction}
When cohesion and repulsion (\textit{inter-agent vectors}) are the only field effects creating a swarming effect the number of stable structures that can develop is limited. These structures are either straight edges or partial lattices. Partial lattices can create concave anomalies (dents) and convex anomalies (peaks) in a perimeter~(Fig.~\ref{concave:SwarmStableShape1}). An anomaly is any construct within the swarm that is not a hexagonal lattice or an agent distribution that causes the swarm to deviate from having only convex or flat edges.

@@

\section{Related Work}\label{sec:RelatedWork}

@@

\section{Concave reduction}\label{sec:ConcaveReduction}

@@

When discussing \textit{concave reduction} the concave angle of interest is the relationship between an agent and two of its adjacent neighbours such that the neighbours have no visibility of each other and the neighbour-agent-neighbour relationship produces an angle~$< 180^\circ$. This is unrelated to the aggregate angle used to identify the perimeter type that the agent is a member of. Concave reduction therefore affects both inner~(Fig.~\ref{fig:InnerPerimeter1}) and outer~(Fig.~\ref{fig:OuterPerimeter1}) perimeter agents. Fig.~\ref{fig:OuterPerimeter1} and \ref{fig:InnerPerimeter1} show candidate agents identified by this process in black.

@@

The purpose of \textit{concave reduction} is to alter the overall structure of the swarm by replacing the calculated \textit{movement-direction vector} on anomalous perimeter agents. These perimeter based changes cause a cascading movement within the swarm as non-perimeter based agent's \textit{interaction vectors} attempting to move towards a position of equilibrium to their neighbours. The movement of the concave-perimeter~(internal void) agents creates a tendency for the void to be removed~(Fig.~\ref{fig:InnerPerimeter2}~and~\ref{fig:InnerPerimeter3}) by percolating the void out of the swarm. On the outer perimeter deformities (indents) are straightened~(Fig.~\ref{fig:OuterPerimeter3}) and eventually a perimeter agent and its neighbours will tend towards creating a convex edge.

@@

% \begin{equation}
% S_b \buildrel \Delta \over = \{(b',\angle\{(b'~b~b^0)) : b' \in nbr(b)\}\}
% \label{eq:ConcaveVoidPhysics1}
% \end{equation}
